DRAFT

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

### • Distance
### 75% of the hotels are located between 0 and 2.4 miles from the main city center. 
### The histogram below shows the distribution of the distances from the city center, the limit for x-axis was set at 25 miles.
```{r echo=FALSE}
ggplot(data=df2, aes(x=distance)) + geom_histogram(fill='navyblue', color='white', bins = 35) + 
  labs(x='Distance', y='Count')
```

@@

### • Trueprice
### 99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
### The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
```{r echo=FALSE, message=FALSE}
ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
  labs(x='Price fpr one night (in EUR)', y='Count') + xlim(0, 600) 
```

@@

### • Accommodation type
### There are 16 unique accommodation types in the dataset. The most numerous types are "Hotel",  "Apartment", "Guest House",  and "Bed and Breakfast". Together they make up 93% of all records.
```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars.There are also 15889 missing values. They appeared, because the hotels with 0 stars were not used for the 'class' variable, as the mean price for them is higher than for places with 1, 1.5, 2, and 2.5 stars, which does not make sense. Therefore, these observations were omitted.
```{r echo=FALSE}
kable(count(df2, class)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### • Weekend and holiday
### 36193 records were made on weekends (66%),  and 18754 - on weekdays (34%)

@@

### Only 21% (11728) of all observations were made on holidays.

@@

## 1.3 Findings. 
### For this project, we wanted to find the best deal among different types of accommodation in Central European countries. 
### Consequently, we formulated the question: 
* *How does the average price change for different values of explanatory variables?*

@@

### • Plot for diff years diff countries
```{r}
df3 <- aggregate(trueprice ~ country + year, 
                 data=df2, 
                 function(x) { 
                   c(mean_price = mean(x)) 
                 })
ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
  geom_bar(stat='identity') + facet_wrap(~country) +
  geom_text(aes(label = round(trueprice)), vjust = -0.2) +
  scale_x_discrete() + ylim(0, 195) + 
  labs(x='Year(2017,2018)', y='Price for one night (in EUR)', fill='Country')
```

@@

>>>>

### There are prominent outliers for *distance* and *true price* variables, therefore, the dataset was transformed, setting the maximum values at the 99% percentile (35 miles and 600 EUR respectively).

```{r echo=FALSE}
df2 <- df2 %>% filter(distance < 35) %>% filter(trueprice < 600)
datasummary(distance + trueprice ~ mean + Min + Max + SD, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```

### • Distance
### 75% of the hotels are located between 0 and 2.4 miles from the main city center. 
### The histogram below shows the distribution of the distances from the city center.

```{r echo=FALSE}
ggplot(data=df2, aes(x=distance)) + geom_histogram(fill='navyblue', color='white', bins = 35) + 
  labs(x='Distance from the city center (in miles)', y='Count')
```

@@

### • Trueprice
### The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.

```{r echo=FALSE, message=FALSE}
ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
  labs(x='Price for one night (in EUR)', y='Count') + xlim(0, 600) 
```

@@

### • Accommodation type
### There are 16 unique accommodation types in the dataset. The most numerous types are "Hotel",  "Apartment", "Guest House",  and "Bed and Breakfast". Together they make up 93% of all records.

```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### The most obsevations belong to 'comfort' class, which corresponds to 3 and 3.5 stars, and to 'first class', which corresponds to 4 and 4.5 stars. There are also 15889 missing values. They appeared, because the hotels with 0 stars were not used for the 'class' variable, as the mean price for them is higher than for places with 1, 1.5, 2, and 2.5 stars, which does not make sense. Therefore, these observations were omitted.
```{r echo=FALSE}
kable(count(df2, class)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### • Weekend and holiday
### 35362 records were made on weekends (66%),  and 18478 - on weekdays (34%)

@@

### Only 21% (11546) of all observations were made on holidays.

@@

## 1.3 Findings. 
### For this project, we wanted to find the best deal among different types of accommodation in Central European countries. 
### Consequently, we formulated the following question: 
* *How does the average price for accommodation change for different values of the following variables: year, country, distance, season, class?*

### • How the price for accommodation changed for 7 Central European countries in 2018 in comparison with 2017.
```{r}
df3 <- aggregate(trueprice ~ country + year, 
                 data=df2, 
                 function(x) { 
                   c(mean_price = mean(x)) 
                 })
ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
  geom_bar(stat='identity') + facet_wrap(~country) +
  geom_text(aes(label = round(trueprice)), vjust = -0.2) +
  scale_x_discrete() + ylim(0, 195) + 
  labs(x='Year(2017,2018)', y='Price for one night (in EUR)', fill='Country')
```

### As we can see from the graph, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.

@@

### • Mean price/ distance

```{r echo=FALSE, message=FALSE}
ggplot(df2, aes(x = distance, y = trueprice))+
  stat_summary_bin(fun = 'mean', bins = 80, 
                   geom = 'point', color = 'red',
                   size = 2) + 
  labs(x='Distance from the city center', y='Price for one night(in EUR)')
```

```{r echo=FALSE, message=FALSE}
ggplot(df2, aes(x = distance, y = trueprice))+
  stat_summary_bin(fun = 'mean', bins = 50, 
                   geom = 'point', color = 'red',
                   size = 2) + 
  labs(x='Distance from the city center', y='Price for one night(in EUR)') +
  xlim(0,25)
```

@@

### Weekend
```{r}
ggplot(data=df2, aes(x=weekend, y=trueprice, group=weekend))+
  geom_violin(trim=FALSE, fill='#A4A4A4', color="darkred")+
  geom_boxplot(width=0.1) + theme_minimal() + 
  labs(x="Weekend", y="Price for one night (in EUR)")
```
